Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Wording
Combining multiple specs -> Automatic discover of specs

\subsection{Combinators for expectations}

@@

\subsection{Combining multiple specs}

@@

\begin{quote}
\emph{How about moving this to appendix?}
\end{quote}

\begin{itemize}
\item We create a spec file for each source file
\item By convention, spec files end in Spec.hs
\end{itemize}

>>>>

\subsection{Setting expectations}

@@

\subsection{Automatic discover of specs}

@@

\noindent We think the following are good conventions for organizing specs:
\begin{itemize}
    \item create a separate spec file for each source file
    \item append {\tt Spec.hs} to the name of spec files
\end{itemize}
